COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2020-06-23 main.tex
Fill in missing data in figure 9
Insert missing Dong et. al citation from introduction

Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure. Features such as gaps and asymmetries 
\citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the emission provide 
diagnostics for the physical processes that drive the evolution of the disks. In many gas-rich systems, these gap features are argued to indicate the 
presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally, although the details of gas-dust 
interactions can have strong effects on the resulting morphologies (Dong) (Need to ask aaron which paper he meant to reference here). In gas-poor/debris systems, a giant perturber can also influence the 
structure of the dust continuum emission. For example, a misaligned giant planet can produce nonaxisymmetric features such as warps \citep{2001A&A...370..447A}, highly eccentric perturbers can produce structures through secular interactions 
\citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}, and mean motion resonances (MMRs) can open gaps
\citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.

@@

In figure \ref{fig:alma_profiles}, we show the azumithally-averaged radial profile constructed from the simulated cleaned image from all five 
simulations. In all cases, a bump or a dip feature is clearly visible at the location of the 3:1 and 2:1 MMRs, indicated by the dashed vertical line. 
As mentioned previously, the feature at the 2:1 MMR acts as the actual diagnostic indicator, while the 3:1 resonance is mainly useful for 
determining where the 2:1 MMR is actually located. (Still waiting on Aaron to finish making images for the e2m1 and e2m3 case).

>>>>

Recent observations of circumstellar disks by ALMA have revealed a rich variety of substructure. Features such as gaps and asymmetries 
\citep{2015ApJ...808L...3A, 2016Sci...353.1519P, PhysRevLett.117.251101, 2016ApJ...820L..40A, 2016Natur.535..258C} in the emission provide 
diagnostics for the physical processes that drive the evolution of the disks. In many gas-rich systems, these gap features are argued to indicate the 
presence of a giant planet, either embedded in the disk \citep{2015MNRAS.453L..73D} or orbiting externally, although the details of gas-dust 
interactions can have strong effects on the resulting morphologies \citep{2018ApJ...866..110D}. In gas-poor/debris systems, a giant perturber can also influence 
the structure of the dust continuum emission. For example, a misaligned giant planet can produce nonaxisymmetric features such as warps 
\citep{2001A&A...370..447A}, highly eccentric perturbers can produce structures through secular interactions 
\citep{2014MNRAS.443.2541P, 2015MNRAS.448.3679P}, and mean motion resonances (MMRs) can open gaps
\citep{2015ApJ...798...83N, 2016ApJ...818..159T, 2018ApJ...857....3T}.

@@

In figure \ref{fig:alma_profiles}, we show the azumithally-averaged radial profile constructed from the simulated cleaned image from all five 
simulations. In all cases, a bump or a dip feature is clearly visible at the location of the 3:1 and 2:1 MMRs, indicated by the dashed vertical line. 
As mentioned previously, the feature at the 2:1 MMR acts as the actual diagnostic indicator, while the 3:1 resonance is mainly useful for 
determining where the 2:1 MMR is actually located.
